Community-Conditioned Language Models

### 2020-11-23 paper/paper.tex
related work & introduction

\jp{We want to identify a niche that we want to fill. A quick summary of the state of the art + what is missing.}

In the present work, we investigate linguistic variation across online communities.
Broadly construed, we want to investigate two questions.  First, we
are interested in variation in the level of linguistic complexity
exhibited by different communities.

@@

In this work, we present results using a conditioned neural language models
to model variation between speech communities.
The architecture of these models concatenates a vector representation
of the conditioned variable to the input of the sequence model.
This approach has been applied in various conditioned text generation domains such as 
image captioning \citep{Vinyals2015}, machine translation \citep{Kalchbrenner2013},
but it has not, to our knowledge, been used extensively to study linguistic variation.
There are, however some related methods that have been used to study variation,
and related applications of conditional neural language models.

In the later category, conditional neural language models have been
used to study linguistic change.

\paragraph{Language models for sociolinguistic variation}
\cite{DelTredici2017}

\cite{khan2020reddit}

\paragraph{Pre-trained language models}
- Unsupervised Domain Clusters in Pretrained Language Models https://www.aclweb.org/anthology/2020.acl-main.692/ % 404?

\paragraph{Topic modelling}
Modelling communities is not unlike the classic task of \emph{topic
  modelling}. In topic modelling, one most often want to
\emph{discover} topics. In constrast, we take as a given that a given
message belongs to a given community. However, deep-learning topic
modelling is often built around the idea of a conditioned language
model \citep{Lau2017a}, with a separate topic-discovery module.

% - Discovering Discrete Latent Topics with Neural Variational Inference https://arxiv.org/pdf/1706.00359.pdf

% \paragraph{Vector representations of online communities encode semantic relationships}
% https://www.aclweb.org/anthology/W17-2904.pdf

>>>>

Not only is linguistic variation an object of inquiry in its own right,
but also important to consider in the development of robust, equitable language technology.
Previous work has shown that by taking demographic information into account, 
models can achieve better performance on various standard NLP tasks \citep{Hovy2015,Yang2017},
but little is known about how variation at the level of speech community affects performance.

There is a fair amount of previous work that investigates linguistic variation using computational methods.
However, most of this work considers variation across macro-social categories,
such as gender \citep{Burger2011,Ciot2013,Bamman2014}, age \citep{Nguyen2013}, 
and geographic location \citep{Eisenstein2010,Bamman2014a}.
An exception to this is \citet{DelTredici2017},
who use the modified skip-gram model of \citet{Bamman2014a} to show that lexical semantic
variation occurs across different communities organized around the same topic.

In the present work, we continue this line of 
investigating linguistic variation across online communities.
In contrast to previous work, we investigate variation across speech communities
(rather than macro-social categories), and use context-sensitive sequence models
capable of capturing variation beyond the lexical level.

Broadly construed, we want to investigate two questions.  First, we
are interested in variation in the level of linguistic complexity
exhibited by different communities.

@@

In this work, we present results using a conditioned neural language models
to model variation between speech communities.
The architecture of these models concatenates a vector representation
of the conditioned variable to the input of the sequence model.
This approach has been applied in various conditioned text generation domains such as 
image captioning \citep{Vinyals2015}, machine translation \citep{Kalchbrenner2013},
but it has not, to our knowledge, been used extensively to study linguistic variation.

There are, however, related applications of conditional neural language models.
\citet{Lau2017a} presents a neural language model that jointly learns to predict
words on the sentence-level and represent topics on the document level.
The topic representation is then fed back into the language model, 
improving its performance on next word prediction.
This is similar to how our model improves experiences improved performance
by learning community representations. 
Unlike our model, topics are inferred in an unsupervised way, 
raising the question of whether communities could be identified from 
unlabelled data as well.

Along these lines, \citep{OConnor2010} uses a Bayesian generative model to
infer communities from variation in text data.
In contrast to our work, this model treats words as
independent events, ignoring the structure (and variation) in the
construction of sequences.
It does further suggest, however, that community-level variation
could be modeled in an unsupervised way.
